\subsection{Models with differentiated products}
\subsubsection{Hotelling competition}
With horizontal product differentiation different consumers prefer different products. With
vertical product differentiation all consumers agree which product is preferable.

In Hotelling, consumers are normally distributed on line of unit length, the number of consumer
is normalized to 1. Consumers either buy 1 unit of good, or none. Each consumer obtains gross
utility $v$ from consuming the product. There are 2 firms, one located at 0, one located at 1.
Consumer located at $x$ needs to travel distance $x$ to buy from firm 0 and $1-x$ distance to
buy from firm 1. Transportation costs are $t$ per unit of distance. Marginal costs for both firms
are constant and equal to $c$. From this information it can be concluded that in equilibrium both
firms charge the same price since the game is symmetric.
Suppose firm $i$ charges price $P_i$. Then a consumer located at $x$ buys from firm 0 iff
\begin{align}
	v-P_0-tx>v-P_1-t(1-x)
\end{align}
provided that $v-P_0-tx>0$. Assume entire market is covered: in equilibrium prices are s.t.
everyone consumes. This implies that $v>2t$.

Define a consumer $z$ that is indifferent between buying from 0 or 1. Every consumer located at
$x<z$ buys from 0, every consumer $x>z$ buys from 1. This consumer $z$ is located at
\begin{align}
	P_0+tz                & =P_1+t(1-z)                     \\
	\Longleftrightarrow z & =\frac{1}{2}+\frac{P_1-P_0}{2t}
\end{align}
Total sales for firm 0 equal $z$ and for firm 1 $1-z$. When they charge the same price
$z=\frac{1}{2}$. Profits for firm 0 are:
\begin{align}
	\Pi_0 & = (P_0-c)z                                         \\
	      & =(P_0-c)\left(\frac{1}{2}\frac{P_1-P_0}{2t}\right)
\end{align}
Then we maximize wrt $P_0$ to get reaction function:
\begin{align}
	P_0=R_0(P_1)=\frac{1}{2}(c+t+P_1)
\end{align}
And by symmetry:
\begin{align}
	P_1=R_1(P_0)=\frac{1}{2}(c+t+P_0)
\end{align}
Thus, in equilibrium (by equation the two reaction functions):
\begin{align}
	P_0^* & =P_1^*=c+t          \\
	\Pi_0 & =\Pi_1=\frac{1}{2}t
\end{align}
\subsubsection{The circular city: Salop}
Consumers are located uniformly on the edge of a circle with perimeter equal to 1. Consumers wish to buy
1 unit of good, have valuation $v$ and transport cost $t$ per unit of distance. Each firm is
allowed to locate in 1 location. There is a fixed cost of entry $f$ and marginal costs $c$.
Hence, firm $i$ has profit $(p_i-c)D_i-f$ if it enters (where $D_i$) is the demand it faces, and
0 otherwise.

In the first stage, the firms decide simultaneously whether to enter or not. Let $n$ denote the
number of entering firms. The firms are located equidistant from each other on the edge of the
circle.

This can be solved using backward induction. Assume $n$ firms have entered, and suppose all
firms except firm 0 charge price $p$, then firm 0 charges price $R_0(p)$. In equilibrium,
$R_0(p^*)=p^*$. Let firm 0 have location 0. The location of firm 0's right-hand neighbor is
$\frac{1}{n}$ (firm 1). Consider consumers located between firm 0 and 1. If firm 0 charges
price $p_0$, then the consumer $z_{0-1}$ that is indifferent between firm 0 and 1 is:
\begin{align}
	p_0+tz_{0-1}                & =p+t\left(\frac{1}{n}-z_{0-1}\right) \\
	\Longleftrightarrow z_{0-1} & =\frac{1}{2n}+\frac{p-p_0}{2t}
\end{align}
The same holds for the left-hand side of firm 0, hence its profits are:
\begin{align}
	\Pi_0(p_0,p)=2(p_0-c)\left(\frac{1}{2n}+\frac{p-p_0}{2t}\right)
\end{align}
Maximize w.r.t. $p_0$ to find the reaction function:
\begin{align}
	R_0(p)=\frac{1}{2}\left(p+c+\frac{t}{n}\right)
\end{align}
Then we impose symmetry:
\begin{align}
	p^*=c+\frac{t}{n}\text{ with profits }\Pi^*=\frac{t}{n^2}
\end{align}
Now we move back to stage 1. Firms enter the market as long as profits are positive. Hence,
the number of enterers is s.t.
\begin{align}
	\Pi^*-f=\frac{t}{n^2}-f=0\Longleftrightarrow n^* & =\sqrt{\frac{t}{f}} \\
	\Longrightarrow p^*                              & =c+\sqrt{tf}
\end{align}
Consumer's average transportation cost is $\frac{t}{4n}=\frac{\sqrt{tf}}{4}$. When the entry
cost tends to 0 the number of entering firms tends to infinity and the market price tends
to marginal cost.

A social planner would choose $n$ in order to minimize the sum of fixed cost and transportation
costs: $\underset{n}{\min}\left(nf+\frac{t}{4n}\right)
	\Longrightarrow n=\frac{1}{2}\sqrt{\frac{t}{f}}=\frac{1}{2}n^*$, hence the market generates
too many firms. Similar results hold for quadratic transportation costs.

There are three natural extensions that would make the model more realistic: the
introduction of a location choice, the possibility that firms do not enter simultaneously,
and the possibility that a firm locates at several points in the product space.
\subsubsection{Perloff and Salop}
Suppose there are two firms, $A$ and $B$, and a unit mass of consumers. Consumer $j$ has a
willingness to pay for the product of firm $i\in\{A,B\}$ that is given by $v+\epsilon_{ij}$,
where $\epsilon_{ij}$ is the realization of a r.v. with cumulative distribution function $F$ on
some interval $[0,\Bar{\epsilon}]$, and continuously differentiable density $f$. Assume $v$ is
high enough that all consumers buy in equilibrium. All draws are independent from each other,
$\epsilon_{ij}$ can be interpreted as the match value between product $i$ and consumer $j$.
Assume all firms have constant marginal cost equal to $c$.

Firstly, suppose both firms charge same price $p^*$. This will happen in equilibrium since the
game is symmetric. Then a consumer buys from $A$ whenever $\epsilon_A>\epsilon_B$ and from $B$
otherwise. To find the equilibrium we need to analyze what happens if firm $A$ defects from a
candidate equilibrium $p^*$ by setting some different price. Without loss of generality assume $A$
defects to some $p_A>p^*$. Denote $\Delta\equiv p_A-p^*$. Now, a consumer buys from firm $A$ if
$\epsilon_A-\Delta>\epsilon_B$. Assume for simplicity the $\epsilon$ are drawn from uniform
distribution on $[0,1]$. Then, the total sales of firm $A$ from charging price
$p_A=p^*+\Delta$ equal $q_A=\frac{1}{2}(1-\Delta)^2$. Hence the expected profits of firm $A$ are
\begin{align}
	\pi_A=(p_A-c)q_A
\end{align}
Profit maximization requires:
\begin{align}
	\frac{\partial\pi_A}{\partial p_A} & =(p_A-c)\frac{\partial q_A}{\partial p_A}+q_A=0,
	\text{ with }\label{eq:FOC_perloff_salop}                                             \\
	\frac{\partial q_A}{\partial p_A}  & =-(1-\Delta)
\end{align}
Then if we take first order condition and impose symmetry, $\Delta=0$ and $q_A=\frac{1}{2}$, we get:
\begin{align}
	(p_A-c)(-1)+\frac{1}{2} & =0             \\
	\Longleftrightarrow p^* & =c+\frac{1}{2}
\end{align}

In the model description the assumption that $v$ is high enough s.t. each consumer will buy in
equilibrium was made. We thus need that a consumer with $(\epsilon_A,\epsilon_B)=(0,0)$ would still
be willing to buy. In this case, with $p^*=c+\frac{1}{2}$ this implies $v>c+ \frac{1}{2}$

We can generalize the model for any distribution function $F$. Then:
\begin{align}
	q_A & = \int_\Delta^1\left(\int_0^{\epsilon_A-\Delta}f(\epsilon_B)\d\epsilon_B\right)f(\epsilon_A)\d\epsilon_A \\
	    & = \int_\Delta^1F(\epsilon_A-\Delta)f(\epsilon_A)\d\epsilon_A
\end{align}
Using Leibnitz' rule, this implies:
\begin{align}
	\frac{\partial q_A}{\partial p_A}=-\int_\Delta^1f(\epsilon_A-\Delta)f(\epsilon_A)\d\epsilon_A
	\label{eq:pa_leibnitz}
\end{align}
Again we can find the equilibrium price by taking first-order condition (\ref{eq:FOC_perloff_salop})
and using (\ref{eq:pa_leibnitz}). In equilibrium $\Delta=0$ and $q_A= \frac{1}{2}$. This yields:
\begin{align}
	p^*=c+\frac{1}{2\int_0^1f^2(\epsilon)\d\epsilon}
\end{align}
Note that the Perloff-Salop model is similar in spirit to the Hotelling model, in the
sense that each consumer has a certain valuation for each firm’s product. The crucial
difference is that in the Hotelling model, these valuations are perfectly negatively cor-
related: a consumer that has a very high valuation for product A, say, necessarily has
a very low valuation for product B, and vice-versa. In the Perloff-Salop model, these
valuations are independent of each other. A consumer with a high valuation for product
A may very well have a high valuation for product B as well. This also implies that the
Perloff-Salop model can easily be generalized to more than 2 firms.
